Modelling the City of Melbourne Pedestrian Data

### 2017-10-03 presentation/final.Rmd
fixed typo in slide 24, updated pseudo transcript
added slides for question prep

- perform simulations to test imputation algorithm for robustness
- explore predictions outside of counts data

@@

>>>>

- perform simulations to test imputation algorithm for robustness
- explore predictors outside of counts data

@@

---
## Proportion of missing values prior to correction:

```{r, fig.retina = 3, fig.align= 'center'}
na_prop_bad <- numeric()

for (i in unique(ped_data$Sensor)){
  na_prop_bad[i] <- sum(is.na(original_df[, i])) / n_obs
}

ggplot() + geom_histogram(aes(x = na_prop_bad*100), bins = 12) +
          xlab("Percentage of Missing Values (%)") +
          ylab("Number of Sensors") + theme_minimal() +
          geom_vline(xintercept = 10, size = 2,
                     colour = 'red') +
          geom_text(aes(label = "10% Threshold", x = 10, y = 1),
                    colour = "white") +
          ggtitle("Histogram of Proportions of Missing Values \n during 2014 - 2016 prior to correction") +
          theme(plot.title = element_text(hjust = 0.5))
```
